---
title: "Memory test on Drugged Islanders"
author: "Dhruv Gupta"
date: '`r Sys.Date()`'
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction
An experiment on the effects of anti-anxiety medicine on memory recall when being primed with happy or sad memories. The participants were done on novel Islanders whom mimic real-life humans in response to external factors.

Drugs of interest (known-as) [Dosage 1, 2, 3]:

A - Alprazolam (Xanax, Long-term) [1mg/3mg/5mg]

T - Triazolam (Halcion, Short-term) [0.25mg/0.5mg/0.75mg]

S- Sugar Tablet (Placebo) [1 tab/2tabs/3tabs]

### Dataset
Source:
https://www.kaggle.com/datasets/steveahn/memory-test-on-drugged-islanders-data

## Driving Questions
* How does anti-anxiety medicine affect you differently by age?

* Is there a level of plateauing in effectiveness of anti-anxiety medicine - if so, at what point?

* Effect of anti-anxiety medicine on memory recall?

## Process Data
```{r, echo=TRUE}
library(readr)
library(tidyverse)
df <- read.csv("Z:\\Dhruv\\Case study\\Islander_data.csv")
head(df)
summary(df)
```

## Analysis
``` {r, echo=TRUE}
ggplot(data = df, mapping = aes(x = Drug, fill = Drug))+
  geom_bar()
```

Even distribution of drugs in the dataset
```
diff_by_age <- df %>% mutate(age_range = cut(age, c(24,34,44,54,64,74,85))) %>% 
  group_by(age_range) %>% 
  summarise_at(vars(Diff), list(Diff = mean))
diff_by_age
```
Age group 34-54 is most affected by the drugs, while age group 55-74 is least affected.
``` {r, echo=TRUE}

ggplot(data = df, mapping = aes(x = age, y = Mem_Score_Before))+
  geom_col()
ggplot(data = df, mapping = aes(x = age, y = Mem_Score_After))+
  geom_col()
ggplot(data = df, mapping = aes(x = Mem_Score_Before, y = Mem_Score_After))+
  geom_jitter()+
  geom_smooth()+
  facet_wrap(vars(Drug))
ggplot(data = df, mapping = aes(x = Mem_Score_Before, y = Mem_Score_After))+
  geom_jitter()+
  geom_smooth()+
  facet_wrap(vars(Happy_Sad_group))
ggplot(data = df, mapping = aes(x = Mem_Score_Before, y = Mem_Score_After,color = Happy_Sad_group))+
  geom_jitter()+
  geom_smooth()+
  facet_wrap(vars(Drug))
ggplot(data = df, mapping = aes(x = age, y = Diff))+
  geom_jitter()+
  geom_smooth()+
  facet_wrap(vars(Drug))+
  labs(caption = 'Drug A has most effect on memory recall, while drug T shows least effect.')
```